# Language analysis

```{r setup, include=FALSE}
# Global options
# library(knitr)
# opts_chunk$set(fig.path="/")
```



## Top languages

Top languages according to title count in each “national” context 


```{r top_language, echo=FALSE, message=FALSE, warning=FALSE, out.width="25%"}

# Combine language data from catalogs
df <- NULL
for (ctl in names(catalogs)) {
  tmp <- catalogs[[ctl]][, c("language_primary", "publication_country")]
  tmp$catalog <- rep(ctl, nrow(tmp))
  df <- dplyr::bind_rows(df, tmp) %>%
          mutate(catalog=toupper(catalog))
}
df$catalog <- factor(df$catalog)

# For each country, show top languagues
ntop <- 5
for (country in unique(df$publication_country)) {

  dfs <- subset(df, publication_country == country)
  ctl <- paste(unique(dfs$catalog), collapse = "+")
  library(comhis)
  library(ggplot2)  
  p <- top_plot(dfs$language_primary, ntop = ntop) +
       labs(title = country, subtitle = ctl) +       
       scale_y_log10() +
       theme_comhis("discrete", base_size=25)
       
  print(p)

}
```


## Top languages by town

Top languages by town (based on the indicated catalog).

```{r top_language_by_town, echo=FALSE, message=FALSE, warning=FALSE, out.width="33%", fig.width=10, fig.height=7}
# Combine language data from catalogs
df <- NULL
for (ctl in names(catalogs)) {

  tmp <- catalogs[[ctl]][, c("language_primary", "publication_country",
                             "publication_place", "publication_decade", "publication_year")]
  tmp$catalog <- rep(ctl, nrow(tmp))
  df <- dplyr::bind_rows(df, tmp) 
}
df <- df %>% mutate(catalog=toupper(catalog))
df$catalog <- factor(df$catalog)

# For each country, show top languagues
ntop <- 5
for (i in seq_len(nrow(selected.towns))) {

  ctl <- toupper(selected.towns[i, "catalog"])
  town <- selected.towns[i, "town"]

  # Pick the selected town and catalog
  dfs <- subset(df, publication_place == town & catalog == ctl)
  
  library(comhis)
  library(ggplot2)  
  p <- top_plot(dfs$language_primary, ntop = ntop) +
       labs(title = town, subtitle = ctl) +
       scale_y_log10() +
       theme_bw(30)
       
  print(p)

}
```



## Top-N languages by town by decade


```{r top_language_by_town_by_decade, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", fig.width=15, fig.height=7}
# Language level ordering
langs <- names(rev(sort(table(df$language_primary))))

# For each place, show top languagues
library(dplyr)
ntop <- 4
for (i in seq_len(nrow(selected.towns))) {

  ctl <- toupper(selected.towns[i, "catalog"])
  town <- selected.towns[i, "town"]

  # Pick the selected town and catalog
  dfs <- subset(df, publication_place == town & catalog == ctl)

  # Top languages for this catalog and place
  dfs$language_primary <- compress_field(dfs$language_primary,
                            topn = 4, rest = "Other")

  # Group by decade
  dfs <- dfs %>% group_by(publication_decade,
                          publication_place,
			  language_primary) %>%
                 summarise(n = n()) %>%
		 group_by(publication_decade, publication_place) %>%
		 arrange(desc(n)) %>%
		 mutate(rank = rev(rank(n))) %>%
		 filter(rank <= ntop)

   # Arrange levels by rank
   dfs$language_primary <- droplevels(factor(dfs$language_primary))

   # Replace NA with 0
   dfs$n[is.na(dfs$n)] <- 0

  library(comhis)
  library(ggplot2)
  p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
         geom_bar(aes(fill = language_primary),
	          position = "stack", stat = "identity") + 
         labs(title = town, subtitle = ctl, y = "Title count (n)") +
         theme_comhis("discrete", base_size=30) +
	 labs(x = "Publication decade", fill = "Primary language") 
  print(p)

}
```



## Language shares per decade until 1800

Stacked histogram of language shares per decade until 1800

```{r language_shares_till_end, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", fig.width=15, fig.height=7}

# For each place, show top languagues
library(dplyr)
ntop <- 4
for (i in seq_len(nrow(selected.towns))) {

  ctl <- toupper(selected.towns[i, "catalog"])
  town <- selected.towns[i, "town"]

  # Pick the selected town and catalog
  dfs <- df %>% filter(publication_place == town & catalog == ctl) %>%
                filter(publication_decade <= 1800)

  # Top languages for this catalog and place
  dfs$language_primary <- compress_field(dfs$language_primary, topn = ntop, rest = "Other")

  # Group by decade
  dfs <- dfs %>% group_by(publication_decade, publication_place, language_primary) %>%
                 summarise(n = n()) %>%
		 mutate(f = n/sum(n)) %>%
		 group_by(publication_decade, publication_place) %>%
		 arrange(desc(n)) %>%
		 mutate(rank = rev(rank(n))) %>%
		 filter(rank <= ntop)

   # Arrange levels by rank
   dfs$language_primary <- droplevels(factor(dfs$language_primary))

   # Replace NA with 0
   dfs$n[is.na(dfs$n)] <- 0

  p <- ggplot(dfs, aes(x = publication_decade, y = f)) +
         geom_bar(aes(fill = language_primary),
	              position = "stack",
		      stat = "identity") +
         scale_y_continuous(label = scales::percent) + 
         labs(title = town,
	      subtitle = ctl,
	      y = "Title share (%)",
	      x = "Publication decade",
	      fill = "Primary language") +
         theme_comhis("discrete", base_size=30) 
  print(p)


}




# Top three languages per year until 1800

```{r language_shares_by_year_till_1800, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", fig.width=15, fig.height=7}
# For each place, show top languagues
library(dplyr)
ntop <- 3
for (i in seq_len(nrow(selected.towns))) {

  ctl <- toupper(selected.towns[i, "catalog"])
  town <- selected.towns[i, "town"]

  # Pick the selected town and catalog
  dfs <- df %>% filter(publication_place == town & catalog == ctl) %>%
                filter(publication_year <= 1800)

  # Top languages for this catalog and place
  dfs$language_primary <- compress_field(dfs$language_primary, topn = ntop, rest = "Other")

  # Group by decade
  dfs <- dfs %>% group_by(publication_year, publication_place, language_primary) %>%
                 summarise(n = n()) %>%
		 mutate(f = n/sum(n)) %>%
		 group_by(publication_year, publication_place) %>%
		 arrange(desc(n)) %>%
		 mutate(rank = rev(rank(n))) %>%
		 filter(rank <= ntop)

   # Arrange levels by rank
   dfs$language_primary <- droplevels(factor(dfs$language_primary))

   # Replace NA with 0
   dfs$n[is.na(dfs$n)] <- 0

   v <- seq(min(na.omit(df$publication_decade)), 1800, 20)
   p <- ggplot(dfs, aes(x = publication_year, y = n)) +
         geom_point(aes(color = language_primary,
	                fill = language_primary)) +
         geom_smooth(aes(fill = language_primary,
	        	 color = language_primary)) +
         scale_x_continuous(breaks = v, labels = v) +			 
         labs(title = town,
	      subtitle = ctl,
	      y = "Title count (n)",
	      x = "Publication year",
	      color = "Primary language") +
	 guides(fill="none", position = "") +
         theme_comhis("discrete", base_size=30) 
  print(p)
}
```


### Latin share 1500-1800

```{r latin_share, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.width=15, fig.height=6}
filter <- dplyr::filter
dfs <- df %>% filter(publication_year >= 1500) %>%
              filter(publication_year < 1800) %>%	      
	      group_by(catalog, publication_year, language_primary) %>%
	      summarise(n=n()) %>%
	      mutate(f=n/sum(n)) %>%
	      filter(language_primary=="Latin") %>%
	      mutate(catalog = toupper(catalog))

# Catalog default colors
cols <- default_colors("catalog")[unique(toupper(dfs$catalog))]
p <- ggplot(dfs, aes(x = publication_year, y = f,
                     color=catalog, fill=catalog)) +
       geom_smooth() +
       # geom_point() +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication year", y = "Latin share (%)") +
       scale_y_continuous(label=scales::percent, limits=c(0,1)) +
       scale_colour_manual(values=unname(cols)) +
       scale_fill_manual(values=unname(cols)) +
       labs(title="Title share", fill="Catalog", color="Catalog")

p1 <- p


filter <- dplyr::filter
dfs <- df %>% filter(publication_year >= 1500) %>%
              filter(publication_year < 1800) %>%	      
	      group_by(catalog, publication_year, language_primary) %>%
	      summarise(n=n()) %>%
	      filter(language_primary=="Latin") %>%
	      mutate(catalog = toupper(catalog))

# Catalog default colors
cols <- default_colors("catalog")[unique(toupper(dfs$catalog))]
p <- ggplot(dfs, aes(x = publication_year, y = n,
                     color=catalog, fill=catalog)) +
       geom_smooth() +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication year", y = "Latin titles (n)") +
       # scale_y_continuous(label=scales::percent, limits=c(0,1)) +
       scale_colour_manual(values=unname(cols)) +
       scale_fill_manual(values=unname(cols)) +
       labs(title="Title count", fill="Catalog", color="Catalog")

p2 <- p


library(patchwork)
p1 + p2
```




### SNB analysis

```{r snblang, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", fig.width=8, fig.height=8}
mylang <- c("Latin", "French")
catalog <- "snb"
df <- catalogs[[catalog]]
df$language_primary <- as.character(df$language_primary)
dfs <- df %>% mutate(language_primary = factor(replace(language_primary, !language_primary %in% mylang, "Other"))) %>%
              filter(publication_year >= 1500) %>%
              filter(publication_year < 1800) %>%
	      group_by(publication_year, language_primary) %>%
	      summarise(n=n()) %>%
	      mutate(f=n/sum(n)) %>%
              filter(language_primary %in% mylang) 


for (lang in mylang) {
  dfss <- dfs %>% filter(language_primary %in% lang)
  
  p <- ggplot(dfss, aes(x = publication_year, y = f)) +
       geom_smooth() +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication year", y = "Share (%)") +
       scale_y_continuous(label=scales::percent) +
       labs(title="Title share", subtitle=paste(catalog, lang, sep = "/"), color="Primary language")
  print(p)


  p <- ggplot(dfss, aes(x = publication_year, y = n)) +
       geom_smooth() +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication year", y = "Title count (N)") +
       labs(title="Title count (N)", subtitle=paste(catalog, lang, sep = "/"), color="Primary language")
  print(p)
}
```



### French analysis

French share in all catalogs.


```{r french, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", fig.width=8, fig.height=8}
mylang <- c("French")

dat <- NULL
for (catalog in setdiff(names(catalogs), c("fnb", "stcv"))) {

  df <- catalogs[[catalog]]
  df$language_primary <- as.character(df$language_primary)
  dfs <- df %>% mutate(language_primary = factor(replace(language_primary,
                       !language_primary %in% mylang, "Other"))) %>%
              filter(publication_decade >= 1600) %>%
              filter(publication_decade < 1800) %>%
	      group_by(publication_decade, language_primary) %>%
	      summarise(n=n()) %>%
	      mutate(f=n/sum(n)) %>%
              filter(language_primary %in% mylang) 

  dfss <- dfs %>% filter(language_primary %in% mylang)
  dfss$catalog <- rep(catalog, nrow(dfss))
  dat <- bind_rows(dat, dfss)
 

}
dat$catalog <- factor(toupper(dat$catalog))

cols <- default_colors("catalog")[levels(dat$catalog)]
p <- ggplot(dat, aes(x = publication_decade, y = f,
            color=catalog, fill=catalog)) +
       geom_smooth() +
       geom_point() +       
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication decade", y = "Share (%)") +       
       scale_y_continuous(label=scales::percent) +
       
       labs(title="Title share",
            subtitle=mylang,
            color="Catalog",
	    fill="Catalog")
print(p)


p <- ggplot(dat, aes(x = publication_decade, y = f,
            color=catalog, fill=catalog)) +
       geom_bar(stat="identity", position="dodge") +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication decade", y = "Share (%)") +       
       scale_y_continuous(label=scales::percent) +
       
       labs(title="Title share",
            subtitle=mylang,
            color="Catalog",
	    fill="Catalog")
print(p)


p <- ggplot(dat, aes(x = publication_decade, y = n,
            color=catalog, fill=catalog)) +
       geom_bar(stat="identity", position="dodge") +
       theme_comhis("discrete", base_size=20) +
       labs(x = "Publication decade", y = "Title count (n)") +              
       labs(title="Title count",
            subtitle=mylang,
            color="Catalog",
	    fill="Catalog")
print(p)
```

### Version info

```{r}
sessionInfo()
```

